---
output:
html_document: default
pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
require(maxLik)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
library(readr)
source("imagematrix.R")
```

```{r load bright.data}
load("../../Data/bright.Rdata")
```

Assignment 4
The assignment consists in producing a report (text, code, plots, and images) about the two following topics.

1. Consider the Rayleigh distribution characterized by the probability density function
$$
f_x(x;\delta^2)=\frac{x}{\delta^2}exp{(-x^2/(2\delta^2))}1_{R_+(x)}
$$
where σ > 0. This is a model for amplitude SAR data.

1.1 Knowing that $E X = σ \sqrt{π/2}$ and that $Var X = σ^2(4 − π)/2$, obtain two estimators for σ2 based on analogy: one of them $\hat σ^2_1$ based on the first sample moment.

1.2 Obtain $\hat σ^2_{ML}$ the maximum likelihood estimator of σ2.

1.3 Compare the performance of $\hat σ^2_1$, $\hat σ^2_{ML}$, and $\hat σ^2$ the improved version of $\hat σ^2_1$ by bootstrap.

2. Define a phantom (different from the ones we saw), define a data model for this phantom, produce one observation, and analyze the effect of the mean and median filters on this image.

作业4作业包括生成有关以下两个主题的报告（文本，代码，图解和图像）。

 1.考虑以概率密度函数为特征的瑞利分布其中σ>0。

$$
f_x(x;\delta^2)=\frac{x}{\delta^2}exp{(-x^2/(2\delta^2))}1_{R_+(x)}
$$

这是幅度SAR数据的模型。

1.1知道$ EX =σ\sqrt {π/ 2} $并且$ Var X =σ^ 2（4 −π）/ 2 $，

根据类推获得σ2的两个估计量：其中一个$ \hat σ^ 2_1 $基于第一个采样时刻。

1.2获得$ \hat σ^ 2_ {ML} $σ2的最大似然估计。

1.3比较bootstrap的$ \hat σ^ 2_1 $，和不使用bootstrap的$ \hat σ^ 2_ {ML} $和$ \hat σ^ 2 $的性能。

2.定义一个模型（不同于我们看到的模型），为该模型定义一个数据模型，产生一个观察结果，并分析均值和中值滤波器对该图像的影响。

we can know that:

the moment estimation of σ is:
$$
\hat σ^2_1=\frac{E(x)^2}{\pi/2}
$$
the maximum likelihood of σ is:
$$
\hat σ^ 2_ {ML}=\frac{\sum_{i=1}^{n} x_i^2}{2n}
$$


```{r Moments estimators}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))
pi = 3.1415926
m = mean(bright.v)
delta2 = m^2/(pi/2)
delta = sqrt(delta2)
print(paste("delta", delta))
f <- function(x, delta){x/(delta^2)*exp(0)^(-(x^2)/(2*(delta^2)))}
x <- seq(0, 5000000, length.out=5000)
y = f(x, delta)

y.df = data.frame(as.vector(y))
xy.df<-data.frame(x=x,y)

ggplot(xy.df,aes(x=x,y))+
  geom_line(colour="green", size=2)+
  scale_x_log10()
```
```{r Maximum likelihood estimators}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))
pi = 3.1415926
m2 = mean(bright.v^2)
delta2 = m/2
delta = sqrt(delta2)
print(paste("delta", delta))
f <- function(x, delta){x/(delta^2)*exp(0)^(-(x^2)/(2*(delta^2)))}
x <- seq(0, 5000000, length.out=5000)
y = f(x, delta)

y.df = data.frame(as.vector(y))
xy.df<-data.frame(x=x,y)

ggplot(xy.df,aes(x=x,y))+
  geom_line(colour="green", size=2)+
  scale_x_log10()
```





```{r Moments estimators improved by bootstrap}
bright.v = as.vector(bright)
bright.df = data.frame(as.vector(bright))

Estimator.delta <- function(z) {
  m = mean(z)
  delta2 = m^2/(pi/2)
  delta = sqrt(delta2)
  return(list("delta"=delta))
}

### Bootstrap improved ML for the GI0 model
n = 300
delta.bootstrap <- array((1:n))
n <- 5661
for(r in 1:n) {
  z <- sample(bright, n, replace=TRUE) 
  estim.bright.delta <- Estimator.delta(z)
  delta.bootstrap[r] = estim.bright.delta
}
delta.bootstrap.matrix = matrix(as.matrix(unlist(delta.bootstrap)))

delta.bootstrap.improved <- mean(delta.bootstrap.matrix)
print(paste("delta.bootstrap.improved", delta.bootstrap.improved))

f <- function(x, delta){x/(delta^2)*exp(0)^(-(x^2)/(2*(delta^2)))}
x <- seq(0, 5000000, length.out=5000)
y = f(x, delta.bootstrap.improved)

y.df = data.frame(as.vector(y))
xy.df<-data.frame(x=x,y)

ggplot(xy.df,aes(x=x,y))+
  geom_line(colour="green", size=2)+
  scale_x_log10()

```

The data of my phantom is produced by python.

Althogh there is a good performance in python for middle value local filter and mean local filter, I still translate the phantom to the type of txt, and rebuild these tow filters by R.

The picture produced by python is in the folder of Data, you may see it if you are interested.

```{r my phantom}

data<-read_delim("../../Data/lishoagang_phantom_t.txt", delim = " ", col_names=FALSE)
data = unlist(data)
data.a= array(data, dim=c(200, 200, 1))
data.n = normalize(data.a)
image = imagematrix(data.n)
plot(image)
```


```{r}
mean1 = 0
mean2 = 255
delta1 = 200
delta2 = 200

rows = 200
cols = 200

data<-read_delim("../../Data/lishoagang_phantom_t.txt", delim = " ", col_names=FALSE)
data = unlist(data)

for(i in 0:(rows-1))
{
  for(j in 1:cols)
  {
    if(data[i*cols+j]==0)
    {
      data[i*cols+j]=rnorm(1, mean=mean1, sd=delta1)
    }
    else
    {
      data[i*cols+j]=rnorm(1, mean=mean2, sd=delta2)
    }
  }
}
data.a = array(data, dim=c(rows, cols, 1))
data.n = normalize(data.a)
image = imagematrix(data.n)
plot(image)
```

mean local filter
```{r}
SkeletonMean <- function(y, s) {
  
  # Input: the image and the side of the squared support
  
  # Output: filtered image z
  
  # Input image dimensions
  m <- dim(y)[1]
  n <- dim(y)[2]
  
  # Make space for the output image
  z <- y
  
  # Main loop
  margin <- (s+1)/2
  marginm1 <- margin-1
  
  for(k in margin:(m-margin)) {
    for(ele in margin:(n-margin)) {
      sum1 = y[((k-marginm1):(k+marginm1)),((ele-marginm1):(ele+marginm1))]
      z[k,ele] = mean(matrix(as.matrix(sum1), nrow=1))
    }
  }
  return(z)
}

mean_image = data.n
mean_image.df = data.frame(mean_image)

mean_filter_image = SkeletonMean(mean_image.df, 3)
mean_filter_image = matrix(as.matrix(mean_filter_image), nrow=200)
image = imagematrix(normalize(mean_filter_image))
plot(image)
```

middle local filter
```{r}
SkeletonMedian <- function(y, s) {
  
  # Input: the image and the side of the squared support
  
  # Output: filtered image z
  
  # Input image dimensions
  m <- dim(y)[1]
  n <- dim(y)[2]
  
  # Make space for the output image
  z <- y
  
  # Main loop
  margin <- (s+1)/2
  marginm1 <- margin-1
  for(k in margin:(m-margin)) {
    for(ele in margin:(n-margin)) {
      
      values <- y[(k-marginm1):(k+marginm1),(ele-marginm1):(ele+marginm1)]
      
      z[k,ele] = median(values)
    }
  }
  
  return(z)
}
middle_image = data.n
middle_image.df = data.frame(middle_image)

middle_filter_image = SkeletonMean(middle_image.df, 5)
middle_filter_image = matrix(as.matrix(middle_filter_image), nrow=200)
image = imagematrix(normalize(middle_filter_image))
plot(image)
```

