---
title: "Report2 - SAR Course Xidian University"
author: "Li shaogang"
date: "10/18/2020"
header-includes: \usepackage{bm,bbm}
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
```

```{r load bright.Rdata}
# Use your paths
source("./imagematrix.R")
load("../../Data/bright.Rdata")
# Inspect what they are in the Environment window
```

What are we supposed to learn in this part?
• Read an image
• Use the imagematrix library
• Plan, produce, and present EDA results

Recommendations
• EDA assumes as little as possible.
• EDA should come after understanding the problem, and
before starting to model the data.
• Choose well between tables and plots; they are adequate
for different types of information.
• Be parsimonious, but also generous with your reader.
• Every table and plot must be explained in your report.

Assignment II
• Implement the densities of the 𝒦 and 𝒢0 distributions for
intensity data
• Implement random number generators for these
distributions
• Illustrate them, along with the densities of the Gamma
distribution; use with your choices of parameters:
• Plot the densities
• Plot histograms and densities
• Analyze the bright image data
• If you need help translating, use deepl.
• Check your wording, spelling, and sentence construction
with grammarly
• Produce your report as an RMarkdown file that produces a
PDF report; share only the RMarkdown file in your
repository. 3



# gamma distribution
```{r}
x <- seq(.1, 5, length.out=500)
y <- gamma(x)
ggplot(data= NULL, aes(x = x, y = y)) +
  geom_point(color = "darkred")  #添加点
```
# degamma distribution
```{r}
x <- seq(.1, 20, length.out=500)
y1 <- dgamma(x, shape=1, scale=2)
y2 <- dgamma(x, shape=2, scale=2)
y3 <- dgamma(x, shape=3, scale=2)
y4 <- dgamma(x, shape=5, scale=1)
y5 <- dgamma(x, shape=9, scale=0.5)
y6 <- dgamma(x, shape=7.5, scale=1)
y7 <- dgamma(x, shape=0.5, scale=1)

SimilarityDistances <- data.frame(x, y1, y2, y3, y4, y5, y6)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:7,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

#K distribution


```{r}
x <- seq(.1, 20, length.out=500)

K <- function(z, a, j, L)
{
  (2*j*L)*(j*L*z)^((a+L)/2-1)*besselK(2*(sqrt(j*L*z)), a-L)/(gamma(a)*gamma(L))
}
y1 <- K(x, 1, 2, 1)
y3 <- K(x, 3, 2, 1)
y8 <- K(x, 8, 2, 1)

SimilarityDistances <- data.frame(x, y1, y3, y8)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:4,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

#G0 distribution

```{r}
x <- seq(.1, 10, length.out=500)

G <- function(z, a, j, L)
{
  L^L*gamma(L-a)*z^(L-1)/(j^a*gamma(L)*gamma(-a)*(j+L*z)^(L-a))
}
y1 <- G(x, -1.5, 2, 1)
y3 <- G(x, -3, 2, 1)
y8 <- G(x, -8, 2, 1)

SimilarityDistances <- data.frame(x, y1, y3, y8)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:4,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

#random number generators

We are going to get the inverse func of K's Cumulative Distribution Functions, so that we can generate those random number.

But it seem that we can't get the inverse func of K. So...

###test example
```{r}
f1 <- function(x){1+0*x}
f2 <- function(x){integrate(f1, 0, x)}


n = 1000
a <- runif(n, 0, 1)

y <- (1:n)

for(i in (1:n))
{
  x <- f2(a[i])$value
  y[i]<-x
}

z <- data.frame(z = as.vector(y))

```


###test for K
```{r}
K <- function(z, a, j, L)
{
  (2*j*L)*(j*L*z)^((a+L)/2-1)*besselK(2*(sqrt(j*L*z)), a-L)/(gamma(a)*gamma(L))
}
f1 <- function(x){K(x, 1, 2, 1)}
f2 <- function(x){integrate(f1, 0, x)}


n = 1000
a <- runif(n, 0, 20)

y <- (1:n)

for(i in (1:n))
{
  x <- f2(a[i])$value
  y[i]<-x
}

z <- data.frame(z = as.vector(y))

```

#Analysis bright

###The following is the simple statistic characteristic of bright.Rdata.
```{r bright.Rdata}
typeof(bright)
dim(bright)
range(bright)

vector.bright <- data.frame(bright=as.vector(bright))
summary(vector.bright)
```
###boxplot
```{r}
vector.bright <- data.frame(as.vector(bright))

ggplot(vector.bright, aes(x=bright)) +
  geom_boxplot(notch = TRUE)+
  scale_x_log10()

```
###density of bright

```{r}
x <- bright

x <- data.frame(x = as.vector(x))
ggplot(x, aes(x=x)) +
  geom_density(col="green", size=2)+
  scale_x_log10()

```
###try to make sence

```{r}
plot(imagematrix(normalize(log(bright))))
```

```{r LogarithmImageTransformation}

clipping <- function(img, low=0, high=1) {
  img[img < low] <- low
  img[img > high] <- high
  img
}

normalize2 <- function(img) {
  clipping(img - mean(img))
}

plot(imagematrix(normalize2(log(bright))))

```


```{r}
normalize3 <- function(img) {
  a <- quantile(img, 0.75)
  clipping(img - a)
}

plot(imagematrix(normalize3(log(bright))))
```


```{r}
normalize3 <- function(img) {
  a <- quantile(img, 0.90)
  clipping(img - a)
}

plot(imagematrix(normalize3(log(bright))))
```



References
Burchell, J. & Vargas, M. (2017), The Hitchhiker’s Guide to ggplot2,
Leanpub.
URL: https://leanpub.com/hitchhikers_ggplot2
Tufte, E. R. (2001), The Visual Display of Quantitative Information,
2 edn, Graphics Press.
Wickham, H. (2009), ggplot2: Elegant Graphics for Data Analysis,
Springer.
Xie, Y., Allaire, J. & Grolemund, G. (2018), R Markdown: The
Definitive Guide, Taylor Francis Ltd.
URL: https://www.ebook.de/de/product/33698871/yihui_
rstudio_inc_boston_ma_usa_xie_j_j_allaire_garrett_
grolemund_r_markdown.html