---
title: "Report2 - SAR Course Xidian University"
author: 'Lishaogang Ruanhengyu Aimee Wangyuan '
date: "2020/10/18"
output: pdf_document
header-includes: \usepackage{bm,bbm}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(reshape2)
require(ggplot2)
require(ggthemes)
theme_set(theme_minimal())
require(GGally)
require(ggExtra)
```

```{r load bright.Rdata}
# Use your paths
source("./imagematrix.R")
load("../../Data/bright.Rdata")
# Inspect what they are in the Environment window
```

What are we supposed to learn in this part?

* Read an image
* Use the imagematrix library
* Plan, produce, and present EDA results

Recommendations

* EDA assumes as little as possible.
* EDA should come after understanding the problem, and before starting to model the data.
* Choose well between tables and plots; they are adequate for different types of information.
* Be parsimonious, but also generous with your reader.
* Every table and plot must be explained in your report.

Assignment II

* Implement the densities of the 𝒦 and 𝒢0 distributions for intensity data
* Implement random number generators for these distributions
* Illustrate them, along with the densities of the Gamma distribution; use with your choices of parameters:
* Plot the densities
* Plot histograms and densities
* Analyze the bright image data
* If you need help translating, use deepl.
* Check your wording, spelling, and sentence construction with grammarly
* Produce your report as an RMarkdown file that produces a PDF report; share only the RMarkdown file in your repository. 3

# 𝒦 distribution：
-----------------------------------------------------------------------
```{r}
x <- seq(.1, 20, length.out=500)

K <- function(z, a, j, L)
{
  (2*j*L)*(j*L*z)^((a+L)/2-1)*besselK(2*(sqrt(j*L*z)), a-L)/(gamma(a)*gamma(L))
}
y1 <- K(x, 1, 2, 1)
y3 <- K(x, 8, 2, 1)
y8 <- K(x, 20, 2, 1)

SimilarityDistances <- data.frame(x, y1, y3, y8)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:4,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

# G0 distribution：
-----------------------------------------------------------------
```{r}
x <- seq(.1, 10, length.out=500)

G <- function(z, a, j, L)
{
  L^L*gamma(L-a)*z^(L-1)/(j^a*gamma(L)*gamma(-a)*(j+L*z)^(L-a))
}
y1 <- G(x, -1.5, 2, 1)
y3 <- G(x, -3, 2, 1)
y8 <- G(x, -16, 2, 1)

SimilarityDistances <- data.frame(x, y1, y3, y8)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:4,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

# Gamma distribution
-----------------------------------------------------------------
```{r}
x <- seq(.1, 5, length.out=500)
y <- gamma(x)
ggplot(data= NULL, aes(x = x, y = y)) +
  geom_point(color = "darkred")  #添加点
```
# degamma distribution
```{r}
x <- seq(.1, 20, length.out=500)
y1 <- dgamma(x, shape=1, scale=2)
y2 <- dgamma(x, shape=2, scale=2)
y3 <- dgamma(x, shape=3, scale=2)
y4 <- dgamma(x, shape=5, scale=1)
y5 <- dgamma(x, shape=9, scale=0.5)
y6 <- dgamma(x, shape=7.5, scale=1)
y7 <- dgamma(x, shape=0.5, scale=1)

SimilarityDistances <- data.frame(x, y1, y2, y3, y4, y5, y6)

SimilarityDistances.melt <- melt(SimilarityDistances, 
                                 measure.vars=2:7,
                                 value.name = "Transformations",
                                 variable.name = "Transformation"
)

ggplot(SimilarityDistances.melt, 
       aes(x=x, y=Transformations,
           color=Transformation,
           group=Transformation
       ))+
  geom_line(size=3, alpha=.5)+
  geom_line(col='black', size=.2)+
  ylim(c(0, .5))+
  theme_economist()
```

# Random number generators
-----------------------------------------------------------------

We don't know how to generate the random number by taking the ratio of two independent Gamma deviates.

So, we are going to get the inverse func of K's Cumulative Distribution Functions.

But it seem that we can't get the inverse func of K. So...

###test example
```{r}
f1 <- function(x){1+0*x}
#inverse func of f1 is f2
f2 <- function(x){integrate(f1, 0, x)}


n = 1000
a <- runif(n, 0, 1)

y <- (1:n)

for(i in (1:n))
{
  x <- f2(a[i])$value
  y[i]<-x
}

z <- data.frame(z = as.vector(y))
ggplot(z, aes(x=z)) +
  geom_density(col="green", size=2)

```


###test for K
```{r}
K <- function(z, a, j, L)
{
  (2*j*L)*(j*L*z)^((a+L)/2-1)*besselK(2*(sqrt(j*L*z)), a-L)/(gamma(a)*gamma(L))
}
f1 <- function(x){K(x, 1, 2, 1)}
f2 <- function(x){integrate(f1, 0, x)}
#f3 = inverse(f2) 
```


# Exploratory Data Analysis
-----------------------------------------------------------------

The following is the simple statistic characteristic of bright.Rdata.

```{r Quantitative_EDA_Urban}
typeof(bright)
dim(bright)
range(bright)

vector.bright<- data.frame(bright=as.vector(bright))
summary(vector.bright)
```
Move to graphical representations of the data.
```{r}
ggplot(vector.bright, aes(x=bright)) +
  geom_boxplot(notch = TRUE)

ggplot(vector.bright, aes(x=bright)) +
  geom_boxplot(notch = TRUE) +
  geom_rug() +
  scale_x_log10()
```

Histograms
-----------------------------------------------------------------
Histograms of the data complement the information shown by the boxplots.
We will use the Freedman-Diaconis rule for building the histograms.
It consists of using bins of equal size: $\frac32 \text{IQR}(z) / n^{1/3}$.

```{r Graphical_EDA_Urban_Histogram, fig.cap='Histograms', fig.subcap=c('Linear scale', 'Semilogarithmic scale'), out.width = "50%", fig.align = "center"}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="black", fill="white")

ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="black", fill="white") +
  scale_x_log10()
```

"mixing" the second boxplot with the second histogram

```{r Graphical_EDA_BoxplotAndHistogram}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright)),
                 col="black", fill="white") +
  geom_boxplot(aes(y=0.8), width=.1, notch=TRUE) +
  ylab("Density and Boxplot") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
# Try reducing the number of bins
```

* The data are positive
* The data have a very large dynamic range
* The data are strongly asymmetric

It's time to look ad the data in their "natural" domain: as an image.
The "imagematrix" library requires that the data be in $[0,1]$.
It provides a function to accomplish this mapping.

```{r}
plot(imagematrix(normalize(bright)))
```

We hardly see anything.
There are a few very large values that "flatten" most of the observations into very dark shades of gray.
We would like to "use" equally all possible values.
In other words, we would like to have a uniform histogram.

We need some theory to solve this challenge.

Consider the continuous random variable $Z\colon \Omega\to\mathbb R$ with cumulative distribution function $F_Z$.
The random variable $W=F_Z(Z)$ has uniform distribution.

Proof: The cumulative distribution function of $W$ is $F_W(w)=\Pr(W\leq w)=\Pr(F_Z(Z)\leq w)$.
Since $Z$ is continuous, there exists the inverse of its cumulative distribution function, $F^{-1}_Z$.
We can then write 
$F_W(w)=\Pr(F_Z(Z)\leq w) = \Pr(F^{-1}_Z(F_Z(Z)) \leq F_Z^{-1}(w)) = \Pr(Z\leq F^{-1}_Z(w))$, 
which is exactly the cumulative distribution function of $Z$ at $F^{-1}_Z(w)$, so $F_W(w)=F_Z(F^{-1}_Z(w))=w$, which characterizes a uniform random variable on $(0,1)$.

So we only need to apply the cumulative distribution function of the random variable that produced the data to the data themselves and we will obtain samples from the Uniform distribution.
But do we have this function?
Usually we don't, but we can estimate it.

One of the simplest manners to estimate a cumulative distribution function from data $z=(z_1,\dots,z_n)$ is with the empirical cumulative distribution function, or just "empirical function."
It is just the finite approximation of the definition of a cumulative distribution function, and is given by
\begin{equation}
\widehat{F}(t) = \frac1n \#\{j \text{ such that } z_j\leq t\} ,
\end{equation}
where $\#$ denotes the number of elements in the set.

Let us see the original data and its empirical function.

```{r OriginalDataEmpiricalFunction}
ggplot(vector.bright, aes(x=bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.bright))/50,
                 col="black", fill="white") +
  stat_ecdf(col="red") +
  ylab("Density and Empirical function") +
  xlab("Intensity in semilogarithmic scale") +
  scale_x_log10()
```

Let us implement this idea.

```{r HistogramEqualization}
# First, we compute the empirical function
ecdf.bright <- ecdf(unlist(vector.bright))

# Then, we apply this function to the data
eq.bright <- ecdf.bright(unlist(vector.bright))

# Finally, we restore the matrix organization of the data
dim(eq.bright) <- dim(bright)

# And we see the result
plot(imagematrix(eq.bright))
```


Let us now perform an EDA on the equalized data.

```{r EDA_EqualizedData}
summary(as.vector(eq.bright))

vector.eq.bright <- data.frame(eq.bright=as.vector(eq.bright))
                              
ggplot(vector.eq.bright, aes(x=eq.bright)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(vector.eq.bright)),
                 col="black", fill="white") +
  geom_boxplot(aes(y=1.2), width=.1, notch=TRUE) +
  ylab("Density and Boxplot") +
  xlab("Equalized data") 

```

Histogram equalization is one of the most important (and basic) operations in image processing.
Once we have understood how it works, we may use the function already implemented in the imagematrix library.

But\dots\ do we need something "so complicated"?
Cannot we use a simple transformation as, for instance, the logarithm?
Of course we can!

```{r LogarithmImageTransformation}
plot(imagematrix(normalize(log(bright))))
```

change normalize
```{r LogarithmImageTransformation}

clipping <- function(img, low=0, high=1) {
  img[img < low] <- low
  img[img > high] <- high
  img
}

normalize2 <- function(img) {
  clipping(img - mean(img))
}

plot(imagematrix(normalize2(log(bright))))

```


```{r}
normalize3 <- function(img) {
  a <- quantile(img, 0.75)
  clipping(img - a)
}

plot(imagematrix(normalize3(log(bright))))
```

## The effect of the bin size on the histogram

The bin size may have big impact on the histogram and, thus, affect the reader's understanding of the data.
We will see examples of this effect with a sample of size $n=300$.

```{r BinSizeEffect, fig.cap='Histograms', fig.subcap=c('Default bin size', 'Freedmand-Diaconis bin size', "Improved histogram"), out.width = "50%", fig.align = "center"}
x <- data.frame(x = as.vector(log(bright)))

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),
                 col="black", fill="white") +
  ylab("Proportions histogram")

ggplot(x, aes(x=x)) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(x)),
                 col="black", fill="white") +
  ylab("Proportions histogram")

ggplot(x, aes(x=x)) +
  geom_density(col="blue", size=2) +
  geom_histogram(aes(y=..density..),
                 bins=nclass.FD(unlist(x)), 
                 alpha=0.5, fill="#33AADE", color="black") +
  ylab("Histogram and smoothed histogram")

```


## Multivariate data

It is an image with three bands.
Let's look at it as it is, and after equalization (independent by band).

```{r}
plot(imagematrix(equalize_indep(bright)))
```

Now we transform the image data into a data.frame.

```{r ImageIntodataframe}

bright.df <- data.frame(ch1=as.vector(bright[,,1]),
                      ch2=as.vector(bright[,,2]),
                      ch3=as.vector(bright[,,3]))
```

Pairs plot: gives an idea of the relationships between pairs of variables.

```{r PairsPlot}
ggpairs(bright.df)
```

Let us pay more attention to each pair.

```{r PairWithMarginal}
ggMarginal(
  ggplot(bright.df, aes(x=ch1, y=ch2)) +
    geom_point()
)
```

We improve the plot.

```{r PairWithMarginalImproved}
ggMarginal(
  ggplot(bright.df, aes(x=ch1, y=ch2)) +
    geom_point(size=.05) +
    scale_x_log10() +
    scale_y_log10(), 
  type = "densigram"
)

```




